\documentclass[a4paper,11pt]{article}%
\addtolength{\oddsidemargin}{-.5in}
\addtolength{\evensidemargin}{-.5in}
\addtolength{\textwidth}{1in}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{moreverb}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{anysize}
\usepackage{pst-rel-points}
\usepackage{pstricks}
\usepackage{pst-node}
%----------------------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\textbf{#1.} }{\ \rule{0.5em}{0.5em}}
%\renewcommand{\chaptername}{Experiment}

%----------------------------------------------------------
\begin{document}
%\frontmatter
\title{CS738: Assignment \# 3}
\author{}
\date{Due date: {\red 14 March 2012, 23:59:59 Hours}}
\maketitle
\section*{Submission Instructions}
\begin{itemize}
\item Create a single pdf file named
  \psframebox[linestyle=none,fillcolor=yellow,fillstyle=solid]{{\tt assign3\_<your roll
     number>.pdf}}
\item Send it by email to instructor (karkare@cse) and copy
  to both TAs (sbjoshi@cse, pritesh@cse)
\item The subject of the email should be
  \psframebox[linestyle=none,fillcolor=yellow,fillstyle=solid]{{\tt
      [CS738] Assignment 3}}
\item There will be {\bf 20\% penalty} per day for late
  submission. In case the assignment is not submitted within
  {\bf 5 days} of deadline, the penalty will be carried over to the
  next assignment. 
\end{itemize}
\section{Constant Propagation and Folding}
For a programming language with only {\em boolean} type,
boolean constants ({\em TRUE, FALSE}) and boolean  operations
({\em AND, OR, NOT}) design a data flow framework for
constant propagation and folding. The language, obviously,
contains basic constructs like assignment statements, gotos
and conditionals (if-else). 

In the framework, you need to:
\begin{itemize}
\item Handle the distinction between the {\em undefined}
  value, {\bf UNDEF}, and the {\em unseen} value, {\bf
    UNSEEN}.
\item Optimize expressions where {\bf ONE} argument
  determines the result of expression (e.g. {\bf TRUE OR any
    =  any OR TRUE = TRUE}). Do not forget to handle {\bf
    UNDEF} and {\bf UNSEEN} appropriately.
\end{itemize}
Show the result of {\em your} analysis on the following
  program when at the Entry node, x, y and z are initialized
  to (a) UNDEF (b) UNSEEN.
\begin{verbatim}
// Entry:
   ...
L:  if (...) {
        x = y AND z;                   
    } else {
        x = TRUE;
    }

    y = NOT x; 

    if (...) goto L;

// Exit
\end{verbatim}

Is your framework monotonic? distributive?

\section{SSA PRE}
Show all steps in application of SSAPRE algorithm to the
following flow graph (including translation to SSA form for
variables). The expressions of interest are {\em a+b}, {\em
  c-a} and {\em b*d}.
 
\begin{center}

\psset{unit=1mm}
\begin{pspicture}(0,0)(150,-160)
  \psframe(0,0)(150,-160)
  \putnode{b0}{origin}{100}{-5}{\psframebox{ENTRY}}

  \putnode{b10}{b0}{0}{-15}{\psframebox{a = 1}}
  \putnode{b11}{b10}{0}{-15}{\psframebox{b = 2}}

  \putnode{b20}{b11}{0}{-15}{\psframebox{c = a+b}}
  \putnode{b21}{b20}{0}{-15}{\psframebox{d = c-a}}

  \putnode{b30}{b21}{-25}{-15}{\psframebox{d = b*d}}

  \putnode{b40}{b30}{-25}{-15}{\psframebox{d = a+b}}
  \putnode{b41}{b40}{0}{-15}{\psframebox{e = \ldots}}

  \putnode{b50}{b30}{25}{-15}{\psframebox{b = a+b}}
  \putnode{b51}{b50}{0}{-15}{\psframebox{e = c-a}}

  \putnode{b60}{b51}{0}{-15}{\psframebox{a = b*d}}
  \putnode{b61}{b60}{0}{-15}{\psframebox{b = \ldots }}

  \putnode{bx}{b61}{0}{-15}{\psframebox{EXIT}}

  \ncline{->}{b0}{b10}

  \ncline{->}{b11}{b20}
  \ncline{->}{b21}{b30}
  \ncline{->}{b30}{b40}
  \ncline{->}{b30}{b50}
  \ncline{->}{b51}{b60}

  \ncline{->}{b61}{bx}

  \ncline{->}{b10}{b11}
  \ncline{->}{b20}{b21}
  \ncline{->}{b40}{b41}
  \ncline{->}{b50}{b51}
  \ncline{->}{b60}{b61}

  \nccurve[angleA=-135,angleB=135,nodesep=-.2,ncurv=1.8]{->}{b41}{b30}
  \nccurve[angleA=-45,angleB=45,nodesep=-.2,ncurv=1.3]{->}{b51}{b20}
\end{pspicture}
\end{center}

\end{document}
