\documentclass[11pt]{article}
\usepackage{anysize}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{pstricks}
\usepackage{pst-text}
\usepackage{pst-node}
\usepackage{pst-rel-points}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{wrapfig}
\usepackage{fancyvrb}
\newcommand{\answer}[1]{}
%% Page layout
\pagestyle{headings}
\markboth{}{Your Name and Roll Number:}
\begin{document}
\noindent \rule{\textwidth}{.2mm}
\begin{center}
{\large {\bf Quiz-3 CS618} }

Duration: 45 Minutes \hfill Max Marks: 50
\end{center} 
\noindent \rule{\textwidth}{.2mm}
\begin{itemize}
\item Write your name and roll number on the question paper and the
  answer book.
\item No explanations will be provided. In case of a doubt, make
  suitable assumptions and justify.
\item There are 2 questions on 2 pages.
\end{itemize}
\noindent \rule{\textwidth}{.2mm}

\begin{enumerate}
\item ({\bf 15 Marks}) Perform {\bf Flow insensitive Subset-based} and {\bf
  Flow insensitive Equality-based} points-to analysis for
  each of the programs. Show only the {\em final} points-to
  information as points-to graphs.
\hrule
  \begin{verbatim}
(a)  if(...)
        p = &x;
     else
        p = &y;

      x = &a;
      y = &b;
     *p = &c;
     *y = &a;


(b)  if(...)
      y = &b;
     else
     *y = &a;

      p = &x;
      p = &y;
      x = &a;
     *p = &c;
  \end{verbatim}
\vfill\mbox{}
\begin{center} (P.T.O.) \end{center}
%\hrule
\clearpage
\item ({\bf 35 Marks}) In this problem, you have to perform the
  steps given below for {\em Inter-procedural Available
    Expressions} analysis for the expression {\tt a * b} for the
  following program. Assume m() is the main function.
  \newcounter{cline}\setcounter{cline}{0} \newcommand{\nline}{%
    \addtocounter{cline}{1} \thecline.\ } \renewcommand{\nline}{}
  
  \newcommand{\ind}{$\qquad$}
  \renewcommand{\arraystretch}{1.5}
  \begin{center}
    \begin{tabular}{@{}l@{\ind\ind}l@{\ind\ind}l}
      \begin{tabular}[t]{@{}l@{}}
        m() \{ \\ 
        \nline \ind call v() \\
        \nline \ind call u() \\
        \}
      \end{tabular}&
      \begin{tabular}[t]{@{}l@{}}
        u() \{ \\
        \nline   \ind a * b \\
        \ind if(\ldots) then \\
        \nline   \ind\ind call v() \\
        \ind else \\
        \nline    \ind\ind call u() \\
        \}
      \end{tabular}&
      \begin{tabular}[t]{@{}l@{}}
        v() \{ \\
        \ind if(\ldots) then \{\\
        \nline     \ind\ind b = 6 \\
        \nline     \ind\ind a * b \\
        \ind \}\\
        \}
      \end{tabular}
    \end{tabular}
  \end{center}
  Show the following steps to arrive at the answer:
  \begin{enumerate}
\item Draw the inter-procedural flow graph (any one of the two representations discussed in class). Clearly label the nodes, and distinguish the $E^0$ (intra-procedural) and $E^1$ (inter-procedural) edges.
\item For each procedure $p$, show the constraints for $\phi(r_p, n_p)$ for each node $n_p$ in the CFG of the procedure. Recall that $r_p$ is the entry node for procedure $p$. Assume the existence of flow functions $f_0, f_1, id$ etc for the underlying data flow framework.
\item Give the fixed-point solution for $\phi(r_p, n_p)$.
\item List the program points where the expression
  {\tt a * b} is available for the program.
\end{enumerate}
\hfill[Marks Distribution: 5+15+10+5]

\answer{ 
  \input{answer4.tex}
}
\end{enumerate}
\end{document}

